---
title: "Dissolved_nutrients_wdecomp"
author: "Charles T. Bond"
date: "`r Sys.Date()`"
output: html_document
---

##  Summary
This pipeline is for processing dissolved oxygen sensor data.

### Setup
```{r setup, include=FALSE}
options(knitr.duplicate.label = "allow")
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/chunk/Chapter_III_Decomp_assays/data_processing/nutrient_waterqual")


```

It loads the package before it begins or else it gets the error again
```{r, library}
library(tidyverse)
library(scales)
library(lubridate)
```


## Load dissolved oxygen sensor data
```{r}
disnutr <- read.csv("/Users/chunk/Chapter_III_Decomp_assays/data_processing/nutrient_waterqual/NUTR_SE_approach4_20220616_20220809_V1.0.csv")
```

Now that we've loaded in the dissolved nutrient data, it is important to remember the design of the study. `Seperately from the decomposition study,` representative sampling of microbes and dissolved nutrients occured at five transcts in each reach. These transects only partially overlapped with decomposition sites. One water sampling transect in each reach occured around each decomposition site, and at least one water sampling transect was inbetween the decomposition sites in each reach, so n=3 (the two proximal and one inbetween sensor), gives the closest estimation of dissolved nutrients within each reach overall, while the nutrient transect closest to each decomposition site may be used to appoximate dissolved nutients at each decomposition site. 

### for reach averages, select n=3 sites. 
```{r}
disnutrim<- disnutr
#disnutrim<- disnutr[disnutr$siteId=="TLMD3"|disnutr$siteId=="TLMD4"|disnutr$siteId=="TLMD5"|disnutr$siteId=="TLMR1"|disnutr$siteId=="TLMR3"|disnutr$siteId=="TLMR5",]

disnutrim$Treatment<- ifelse(disnutrim$siteId=="TLMD1"|disnutrim$siteId=="TLMD2"|disnutrim$siteId=="TLMD3"|disnutrim$siteId=="TLMD4"|disnutrim$siteId=="TLMD5","Impact","Control")

## a couple non-essential dates have incomplete data, e.g., the day the dam was connected was only top and bottom of each reach.
#disnutrim<- disnutrim[disnutrim$notes!="dam connected",]
#disnutrim<- disnutrim[disnutrim$notes!="1 week connected",]
#disnutrim<- disnutrim[disnutrim$notes!="3 week connected",]
```

now produce table of mean/SD dissolved nutrients by treatment, i.e., reach and timepoint
```{r}

nutrtab <- disnutrim %>%
  group_by(Treatment, date) %>%
  summarise(#date=date,
            #Treatment=Treatment,
            #phase=notes,
    SRPugL = mean(SRPugL),
    sdSRPugL = mean(SRPstd),
    NH4ugL = mean(NH4ugL),
    sdNH4ugL = mean(NH4std),
    NO3NO2ugL = mean(NO3NO2ugL),
    sdNO3NO2ugL = mean(NO3NO2std)
  )
nutrtab

```


```{r}
dam_day<- as.POSIXct("2022-06-27")
undam_day<- as.POSIXct("2022-07-25")
tcol<- c("cornflowerblue","brown1")

nutrtab$date<- as.POSIXct(as.Date(as.character(nutrtab$date),"%Y%m%d"))

dis_SRP <- ggplot(nutrtab, aes(x=date, y=SRPugL, fill=Treatment))+
    geom_bar(position=position_dodge(80000), stat="identity",
           colour='black')+
  ylim(-1.5,16)+
  scale_fill_manual(values = tcol)+
    geom_errorbar(aes(ymin=SRPugL-sdSRPugL, ymax=SRPugL+sdSRPugL),#, colour = Treatment), 
                  position=position_dodge(80000), width=.8)+
  #  scale_color_manual(values = tcol)+
   geom_vline(xintercept = dam_day, linetype="dotted", size = 0.4) +   geom_vline(xintercept = undam_day+hours(6), linetype="dotted", size = 0.4) +
  annotate('text', x=dam_day, y=14.5, label = "\nFlow diversion",  angle=90, size=3)+
  annotate('text', x=undam_day+hours(6), y=14.5, label = "\nFlow restoration",  angle=90, size=3)
dis_SRP

t1min<- as.POSIXct("2022-06-07 18:00:00", tz="UTC")
t1mid<- as.POSIXct("2022-06-27 18:00:00", tz="UTC") - days(10) 
t1max<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")

t2amin<- as.POSIXct("2022-06-22 18:00:00", tz="UTC")
t2amid<- as.POSIXct("2022-07-12 18:00:00", tz="UTC") - days(10) 
t2amax<- as.POSIXct("2022-07-12 18:00:00", tz="UTC")

t2bmin<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")
t2bmid<- as.POSIXct("2022-07-22 6:00:00", tz="UTC") - days(12) 
t2bmax<- as.POSIXct("2022-07-22 18:00:00", tz="UTC")

t3min<- as.POSIXct("2022-07-22 18:00:00", tz="UTC")
t3mid<- as.POSIXct("2022-08-12 6:00:00", tz="UTC") - days(10)
t3max<- as.POSIXct("2022-08-12 18:00:00", tz="UTC")

dis_SRP_annotated <- dis_SRP+
  ## t1
    annotate('rect', xmin = t1min, xmax = t1max, ymin = -0.75, ymax = 0, alpha = 0.7, fill = 'blue', col = 'black')+
  annotate('text', x=t1mid , y=-0.375, label = "t1", size=2.5)+
  ## t2a
    annotate('rect', xmin = t2amin, xmax = t2amax, ymin = -1.5, ymax = -0.75, alpha = 0.7, fill = 'yellow', col = 'black')+
  annotate('text', x=t2amid , y=-1.125, label = "t2a",   size=2.5)+
  ## t2b
    annotate('rect', xmin = t2bmin, xmax = t2bmax, ymin = -0.75, ymax = 0, alpha = 0.7, fill = 'red', col = 'black')+
  annotate('text', x=t2bmid , y=-0.375, label = "t2b",   size=2.5)+
  ## t3
    annotate('rect', xmin = t3min, xmax = t3max, ymin = -0.75, ymax = 0, alpha = 0.7, fill = 'green', col = 'black')+
  annotate('text', x=t3mid , y=-0.375, label = "t3",   size=2.5)
dis_SRP_annotated 

library(ragg)
plotout <- "decomp_phase_SRP.tiff"
agg_tiff(filename=plotout, width=4200, height=2000, units="px",
         pointsize=10, res=600, compression="lzw", scaling=0.5)
dis_SRP_annotated
#plot_grid(nmds2plus,ASVaccumsub,venndiagram,dbRDA_B,dbRDAL,dbRDA_S, labels="AUTO", ncol=3)
invisible(dev.off())

```

NH4
```{r}

#nutrtab$date<- as.POSIXct(as.Date(as.character(nutrtab$date),"%Y%m%d"))
nutrtab$NH4ugL

dis_NH4 <- ggplot(nutrtab, aes(x=date, y=NH4ugL, fill=Treatment))+
    geom_bar(position=position_dodge(80000), stat="identity",
           colour='black')+
  ylim(-4,45)+
  scale_fill_manual(values = tcol)+
    geom_errorbar(aes(ymin=NH4ugL-sdNH4ugL, ymax=NH4ugL+sdNH4ugL),#, colour = Treatment), 
                  position=position_dodge(80000), width=.8)+
  #  scale_color_manual(values = tcol)+
   geom_vline(xintercept = dam_day, linetype="dotted", size = 0.4) +   geom_vline(xintercept = undam_day+hours(6), linetype="dotted", size = 0.4) +
  annotate('text', x=dam_day, y=39, label = "\nFlow diversion",  angle=90, size=3)+
  annotate('text', x=undam_day+hours(6), y=39, label = "\nFlow restoration",  angle=90, size=3)
dis_NH4

dis_NH4_annotated <- dis_NH4+
  ## t1
    annotate('rect', xmin = t1min, xmax = t1max, ymin = -2, ymax = 0, alpha = 0.7, fill = 'blue', col = 'black')+
  annotate('text', x=t1mid , y=-1, label = "t1", size=2.5)+
  ## t2a
    annotate('rect', xmin = t2amin, xmax = t2amax, ymin = -4, ymax = -2, alpha = 0.7, fill = 'yellow', col = 'black')+
  annotate('text', x=t2amid , y=-3, label = "t2a",   size=2.5)+
  ## t2b
    annotate('rect', xmin = t2bmin, xmax = t2bmax, ymin = -2, ymax = 0, alpha = 0.7, fill = 'red', col = 'black')+
  annotate('text', x=t2bmid , y=-1, label = "t2b",   size=2.5)+
  ## t3
    annotate('rect', xmin = t3min, xmax = t3max, ymin = -2, ymax = 0, alpha = 0.7, fill = 'green', col = 'black')+
  annotate('text', x=t3mid , y=-1, label = "t3",   size=2.5)
dis_NH4_annotated 

library(ragg)
plotout <- "decomp_phase_NH4.tiff"
agg_tiff(filename=plotout, width=4200, height=2000, units="px",
         pointsize=10, res=600, compression="lzw", scaling=0.5)
dis_NH4_annotated
#plot_grid(nmds2plus,ASVaccumsub,venndiagram,dbRDA_B,dbRDAL,dbRDA_S, labels="AUTO", ncol=3)
invisible(dev.off())

```

NO3NO2
```{r}

#nutrtab$date<- as.POSIXct(as.Date(as.character(nutrtab$date),"%Y%m%d"))
nutrtab$NO3NO2ugL

dis_NO3NO2 <- ggplot(nutrtab, aes(x=date, y=NO3NO2ugL, fill=Treatment))+
    geom_bar(position=position_dodge(80000), stat="identity",
           colour='black')+
  ylim(-4,40)+
  scale_fill_manual(values = tcol)+
    geom_errorbar(aes(ymin=NO3NO2ugL-sdNO3NO2ugL, ymax=NO3NO2ugL+sdNO3NO2ugL),#, colour = Treatment), 
                  position=position_dodge(80000), width=.8)+
  #  scale_color_manual(values = tcol)+
   geom_vline(xintercept = dam_day, linetype="dotted", size = 0.4) +   geom_vline(xintercept = undam_day+hours(6), linetype="dotted", size = 0.4) +
  annotate('text', x=dam_day, y=34, label = "\nFlow diversion",  angle=90, size=3)+
  annotate('text', x=undam_day+hours(6), y=34, label = "\nFlow restoration",  angle=90, size=3)
dis_NO3NO2

dis_NO3NO2_annotated <- dis_NO3NO2+
  ## t1
    annotate('rect', xmin = t1min, xmax = t1max, ymin = -2, ymax = 0, alpha = 0.7, fill = 'blue', col = 'black')+
  annotate('text', x=t1mid , y=-1, label = "t1", size=2.5)+
  ## t2a
    annotate('rect', xmin = t2amin, xmax = t2amax, ymin = -4, ymax = -2, alpha = 0.7, fill = 'yellow', col = 'black')+
  annotate('text', x=t2amid , y=-3, label = "t2a",   size=2.5)+
  ## t2b
    annotate('rect', xmin = t2bmin, xmax = t2bmax, ymin = -2, ymax = 0, alpha = 0.7, fill = 'red', col = 'black')+
  annotate('text', x=t2bmid , y=-1, label = "t2b",   size=2.5)+
  ## t3
    annotate('rect', xmin = t3min, xmax = t3max, ymin = -2, ymax = 0, alpha = 0.7, fill = 'green', col = 'black')+
  annotate('text', x=t3mid , y=-1, label = "t3",   size=2.5)
dis_NO3NO2_annotated 

library(ragg)
plotout <- "decomp_phase_NO3NO2.tiff"
agg_tiff(filename=plotout, width=4200, height=2000, units="px",
         pointsize=10, res=600, compression="lzw", scaling=0.5)
dis_NO3NO2_annotated
#plot_grid(nmds2plus,ASVaccumsub,venndiagram,dbRDA_B,dbRDAL,dbRDA_S, labels="AUTO", ncol=3)
invisible(dev.off())

```


```{r}
library(cowplot)

bigp<- plot_grid(dis_SRP_annotated , dis_NH4_annotated , dis_NO3NO2_annotated , labels=NA, ncol=1)
bigp

plotout <- "decomp_nutrients.tiff"
agg_tiff(filename=plotout, width=2500, height=4000, units="px",
         pointsize=10, res=600, compression="lzw", scaling=0.5)
bigp
#plot_grid(nmds2plus,ASVaccumsub,venndiagram,dbRDA_B,dbRDAL,dbRDA_S, labels="AUTO", ncol=3)
invisible(dev.off())

```

```{r}
Ctab <- disnutrim[disnutrim$Treatment=="Control",] %>%
  group_by(date) %>%
  summarise(
    SRPugLC = mean(SRPugL),
    sdSRPugLC = mean(SRPstd),
    NH4ugLC = mean(NH4ugL),
    sdNH4ugLC = mean(NH4std),
    NO3NO2ugLC = mean(NO3NO2ugL),
    sdNO3NO2ugLC = mean(NO3NO2std)
  )
Ctab

Itab<- disnutrim[disnutrim$Treatment=="Impact",] %>%
  group_by(date) %>%
  summarise(
    SRPugLI = mean(SRPugL),
    sdSRPugLI = mean(SRPstd),
    NH4ugLI = mean(NH4ugL),
    sdNH4ugLI = mean(NH4std),
    NO3NO2ugLI = mean(NO3NO2ugL),
    sdNO3NO2ugLI = mean(NO3NO2std)
  )
Itab

CI_tab<- merge(Ctab, Itab, by="date")

CI_tab$period<- ifelse(CI_tab$date==20220616, "Before",NA)
CI_tab$period<- ifelse(CI_tab$date==20220628, "After_d1",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220705, "After_wk1",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220712, "After_wk2",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220719, "After_wk3",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220725, "After_wk4",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220726, "Recovery_d1",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220730, "Recovery_d5",CI_tab$period)
CI_tab$period<- ifelse(CI_tab$date==20220809, "Recovery_wk2",CI_tab$period)
CI_tab$period<- factor(CI_tab$period, levels=c("Before","After_d1","After_wk1","After_wk2","After_wk3","After_wk4","Recovery_d1","Recovery_d5","Recovery_wk2"))

lmtest<- summary(lm(SRPugLI~SRPugLC, data=CI_tab))
lmtest
CI_SRP <- ggplot(CI_tab, aes(x=SRPugLC, y=SRPugLI, colour=period))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 3))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_SRP

lmtest<- summary(lm(NH4ugLI~NH4ugLC, data=CI_tab))
lmtest
CI_NH4 <- ggplot(CI_tab, aes(x=NH4ugLC, y=NH4ugLI, colour=period))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 3))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_NH4

lmtest<- summary(lm(NO3NO2ugLI~NO3NO2ugLC, data=CI_tab))
lmtest
CI_NO3NO2 <- ggplot(CI_tab, aes(x=NO3NO2ugLC, y=NO3NO2ugLI, colour=period))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 3))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_NO3NO2

```

```{r}
### check is nutrient data satisfy parametric assumptionms
##### Trying with nonparametric Kruskal Wallis test
disnutrim<- disnutrim %>% mutate(Treatment_time = paste(Treatment, date, sep = '_'))
## a couple non-essential dates have incomplete data, e.g., the day the dam was connected was only top and bottom of each reach.
disnutrim<- disnutrim[disnutrim$notes!="dam connected",]
disnutrim<- disnutrim[disnutrim$notes!="1 week connected",]
disnutrim<- disnutrim[disnutrim$notes!="3 week connected",]

################################ NH4
shapiro_test <- disnutrim %>%
  group_by(as.factor(Treatment_time)) %>%
  summarize(p_value = shapiro.test(NH4ugL)$p.value)
shapiro_test
levene_test1 <- disnutrim %>%
  rstatix::levene_test(NH4ugL~Treatment_time)
levene_test1
# Awesome, NH4 is normal and has equal variance between levels

disnutrim$date<- as.factor(disnutrim$date)
disnutrim$Treatment<- as.factor(disnutrim$Treatment)

library(multcompView)
BACI_NH4_aov<- aov(NH4ugL~Treatment*date,data=disnutrim)
summary(BACI_NH4_aov) ### significant interaction
tukey<- TukeyHSD(BACI_NH4_aov)
tukey
# compact letter display
cld <- multcompLetters4(BACI_NH4_aov, tukey)
cld$`Treatment:date`


################################ NO3/NO2
shapiro_test <- disnutrim %>%
  group_by(as.factor(Treatment_time)) %>%
  summarize(p_value = shapiro.test(log(NO3NO2ugL))$p.value)
shapiro_test
levene_test1 <- disnutrim %>%
  rstatix::levene_test(log(NO3NO2ugL)~Treatment_time)
levene_test1
# Awesome, log-tranformed NO3+NO2 is normal and has equal variance between levels

library(multcompView)
BACI_NO3NO2ugL_aov<- aov(log(NO3NO2ugL)~Treatment*date,data=disnutrim)
summary(BACI_NO3NO2ugL_aov) ### significant interaction
tukey<- TukeyHSD(BACI_NO3NO2ugL_aov)
tukey
# compact letter display
cld <- multcompLetters4(BACI_NO3NO2ugL_aov, tukey)
cld$`Treatment:date`


################################ SRP
# Shapiro-Wilk test for normality
shapiro_test <- disnutrim %>%
  group_by(as.factor(Treatment_time)) %>%
  summarize(p_value = shapiro.test(SRPugL)$p.value)
shapiro_test

## Control_20220809 is non-normal, try log-scale
shapiro_test <- disnutrim %>%
  group_by(as.factor(Treatment_time)) %>%
  summarize(p_value = shapiro.test(sqrt(SRPugL))$p.value)
shapiro_test
## NA, still non-parametric
#################
kruskal.test(SRPugL~Treatment_time,data=disnutrim)

library(FSA)
#perform Dunn's Test with Holm correction for p-values
dt<- dunnTest(SRPugL~Treatment_time,data=disnutrim, method="holm")
library(rcompanion)
dtr<- dt$res
cld <- cldList(comparison = dtr$Comparison,
        p.value    = dtr$P.adj,
        threshold  = 0.05)
cld


```
