---
title: "Dissolved_oxygen_sensor_processing"
author: "Charles T. Bond"
date: "11/12/2024, updated 07/11/2025"
output: html_document
---

##  Summary
This pipeline is for processing dissolved oxygen sensor data.


### Setup
```{r setup, include=FALSE}
options(knitr.duplicate.label = "allow")
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/chunk/Chapter_III_Decomp_assays/data_processing/DO_sensor_data")
```

It loads the package before it begins or else it gets the error again
```{r, library}
library(tidyverse)
library(scales)
library(lubridate)
```


## Load dissolved oxygen sensor data
```{r}
impact_down <- read.csv("/Users/chunk/Chapter_III_Decomp_assays/data_processing/DO_sensor_data/impact_bottom_DO.csv")
impact_up <- read.csv("/Users/chunk/Chapter_III_Decomp_assays/data_processing/DO_sensor_data/impact_top_DO.csv")
control_down<- read.csv("/Users/chunk/Chapter_III_Decomp_assays/data_processing/DO_sensor_data/control_bottom_DO.csv")
control_up <- read.csv("/Users/chunk/Chapter_III_Decomp_assays/data_processing/DO_sensor_data/control_top_DO.csv")

head(control_up)
```

Now we want to take the data from the four sensors and mege them into one dataframe (or tibble), along with important metadata. We will then calculated average dissolved oxygen in each reach over each decomposition assay incubation timeframe.
```{r}
#### Addiing identifiers (site and treatment) to sensor data before merging into one tibble

IDtib <- add_column(impact_down,Location=as.factor("ID")) %>% add_column(Treatment=as.factor("Impact"))

IUtib <- add_column(impact_up,Location=as.factor("IU")) %>% add_column(Treatment=as.factor("Impact"))

CDtib <- add_column(control_down,Location=as.factor("CD")) %>% add_column(Treatment=as.factor("Control"))

CUtib <- add_column(control_up,Location=as.factor("CU")) %>% add_column(Treatment=as.factor("Control"))

dd_allDO<- rbind(IDtib, IUtib, CDtib, CUtib)
head(dd_allDO)
write.csv(dd_allDO, "All_DOsensors_tibble.csv")
```

## Visualization
Now let's take a look at the sensors, make some plots to check it out visually before moving forward with averaging data over incubation phases. 
```{r}
## formatting datetime
dd_allDO$datetime <- as.POSIXlt(dd_allDO$datetime, tz = "UTC", format = "%m/%d/%Y %H:%M")
dd_allDO$datetime<- as.POSIXct(dd_allDO$datetime)+years(2000)
head(dd_allDO)
### focus on dates of the experiment
dd_allDO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-06-14 17:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-08-13 18:00:00", tz="UTC"),]

## sensors were activated in te lab June 11th, and placed a few days later (on te 14th). So we're missing about a week of data as far as the decomposition assays go few days after t1 decomposition assays were deployed.  We'll use the data for the period we have for T1, this should be high DO in any case as it is before the manipulation began.

head(dd_allDO)

```


```{r}
theme_set(theme_bw())

dd_allDO$Location <- factor(dd_allDO$Location, levels=c('CU', 'IU', 'CD', 'ID'))
### labeller for facet
lblr = labeller(Location = 
    c("CU" = "Control reach: upstream sensor",
      "IU" = "Impact reach: upstream sensor",
      "CD" = "Control reach: downstream sensor",
      "ID" = "Impact reach: downstream sensor"))

dry_down_DO <- ggplot(dd_allDO, aes(x=datetime, y=DO_mgL))+
    geom_point(size=0.2)+
    facet_wrap(~Location, nr=2, labeller = lblr)+#+
   # geom_smooth(method='gam', col='red', aes(group=Location))
   theme( #axis.text = element_text( size = 14 ),
           #axis.text.x = element_text( size = 20 ),
           #axis.title = element_text( size = 16, face = "bold" ),
           strip.text = element_text(size = 12, face="bold"))

dry_down_DO
```

Now with graphics to help communicate the experiment timeline...
```{r}

### now with experiment graphics
dam_day<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")
undam_day<- as.POSIXct("2022-07-25 19:00:00", tz="UTC")
t1min<- as.POSIXct("2022-06-07 18:00:00", tz="UTC")
t1mid<- as.POSIXct("2022-06-27 18:00:00", tz="UTC") - days(10) 
t1max<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")

t2amin<- as.POSIXct("2022-06-22 18:00:00", tz="UTC")
t2amid<- as.POSIXct("2022-07-12 18:00:00", tz="UTC") - days(10) 
t2amax<- as.POSIXct("2022-07-12 18:00:00", tz="UTC")

t2bmin<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")
t2bmid<- as.POSIXct("2022-07-22 6:00:00", tz="UTC") - days(12) 
t2bmax<- as.POSIXct("2022-07-22 18:00:00", tz="UTC")

t3min<- as.POSIXct("2022-07-22 18:00:00", tz="UTC")
t3mid<- as.POSIXct("2022-08-12 6:00:00", tz="UTC") - days(10)
t3max<- as.POSIXct("2022-08-12 18:00:00", tz="UTC")

xtmin<- as.POSIXct("2022-06-05 18:00:00", tz="UTC")

dry_down_DO2<- dry_down_DO+
  aes(ymin=-3.8, xmin=xtmin)+
  geom_vline(xintercept = dam_day, linetype="dotted", linewidth = 0.5, color="blue") +   
  geom_vline(xintercept = undam_day, linetype="dotted", linewidth = 0.5, color="blue") +
    annotate('text', x=dam_day, y=10, label = "\nFlow diversion",  #angle=90, 
             size=3, hjust=-0.05)+
  annotate('text', x=undam_day, y=10, label = "\nFlow restoration",  #angle=90, 
           size=3, hjust=-0.05)+
  ### rectangles to represent incubation phases
  ## t1
    annotate('rect', xmin = t1min, xmax = t1max, ymin = -0.5, ymax = -2, alpha = 0.7, fill = 'blue', col = 'black')+
  annotate('text', x=t1mid , y=-1.25, label = "t1", size=3)+
  ## t2a
    annotate('rect', xmin = t2amin, xmax = t2amax, ymin = -2, ymax = -3.5, alpha = 0.7, fill = 'yellow', col = 'black')+
  annotate('text', x=t2amid , y=-2.75, label = "t2a",   size=3)+
  ## t2b
    annotate('rect', xmin = t2bmin, xmax = t2bmax, ymin = -0.5, ymax = -2, alpha = 0.7, fill = 'red', col = 'black')+
  annotate('text', x=t2bmid , y=-1.25, label = "t2b",   size=3)+
  ## t3
    annotate('rect', xmin = t3min, xmax = t3max, ymin = -0.5, ymax = -2, alpha = 0.7, fill = 'green', col = 'black')+
  annotate('text', x=t3mid , y=-1.25, label = "t3",   size=3)+
  ylab(label="Dissolved oxygen (mg/L)")

dry_down_DO2


```

```{r}
library(ragg)
plotout <- "DO_sensor_dataplots_07062025.tiff"
agg_tiff(filename=plotout, width=2100, height=1600, units="px",
         pointsize=10, res=600, compression="lzw", scaling=0.5)
dry_down_DO2
#plot_grid(nmds2plus,ASVaccumsub,venndiagram,dbRDA_B,dbRDAL,dbRDA_S, labels="AUTO", ncol=3)
invisible(dev.off())

#bigp<- plot_grid(#kT_allhab_plotCS, kT_LL_allhab_plot,
#                 #ergo_ug.pgC_CS_BACI_plot, ergo_ug.pgC_LL_allhab_plot,
#                 CN_allhab_plotCS, CN_allhab_plotLL, 
#                 CP_allhab_plotCS, CP_allhab_plotLL,
#                 NP_allhab_plotCS, NP_allhab_plotLL,
#                 labels=c('A','B','C','D' ,'E','F'#,'G','H'
#                          ), ncol=2)
#bigp
#bigpl<- plot_grid(bigp, legend, rel_widths = c(1,0.15),
               #  CN_allhab_plotCS, CN_allhab_plotLL, 
                # CP_allhab_plotCS, CP_allhab_plotLL,
#                  ncol=2)
#bigpl
```



### Calculating dissolved oxygen means for each sensor in each incubation period

#### T1 - Before
NOTE: The first week of DO data for T1
```{r}

t1DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-06-08 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-06-27 05:00:00", tz="UTC"),]
#t1stics <- date_test[date_test$datetime > as.POSIXct("2022-06-07 23:45:00", tz="UTC") & date_test$datetime < as.POSIXct("2022-06-07 23:45:00", tz="UTC")

t1_DO_summmary <- t1DO %>% group_by(Location) %>% summarize(time="t1", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
t1_DO_summmary 
```

#### t2a - Before into flow reduction
```{r}
t2aDO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-06-23 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-12 05:00:00", tz="UTC"),]

t2a_DO_summmary <- t2aDO %>% group_by(Location) %>% summarize(time="t2a", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
t2a_DO_summmary 

```

#### t2b - flow reduction
```{r}
t2bDO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-06-28 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-22 05:00:00", tz="UTC"),]

t2b_DO_summmary <- t2bDO %>% group_by(Location) %>% summarize(time="t2b", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
t2b_DO_summmary 
```

#### t3 - flow restoration phase
```{r}
t3DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-23 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-08-12 05:00:00", tz="UTC"),]

t3_DO_summmary <- t3DO %>% group_by(Location) %>% summarize(time="t3", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
t3_DO_summmary 
```

```{r}
stic_decomptime_summaries<- rbind(t1_DO_summmary, t2a_DO_summmary, t2b_DO_summmary, t3_DO_summmary)
write.csv(stic_decomptime_summaries, "decomp_DO_summaries.csv")

```

### core dry-down
1-week average DO for all 6 time points
```{r}
#T1 NOTE, Control is missing data extending out to a week, but we assume DO was stable during this period due to flowing conditions
T1DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-06-14 18:00:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-06-16 17:45:00", tz="UTC"),]

T1_DO_summmary <- T1DO %>% group_by(Location) %>% summarize(time="T1", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T1_DO_summmary 

#T2
T2DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-05 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-12 05:00:00", tz="UTC"),]

T2_DO_summmary <- T2DO %>% group_by(Location) %>% summarize(time="T2", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T2_DO_summmary 

#T3
T3DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-18 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-25 05:00:00", tz="UTC"),]

T3_DO_summmary <- T3DO %>% group_by(Location) %>% summarize(time="T3", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T3_DO_summmary 

#T4
T4DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-19 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-26 05:00:00", tz="UTC"),]

T4_DO_summmary <- T4DO %>% group_by(Location) %>% summarize(time="T4", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T4_DO_summmary 

#T5
T5DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-23 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-30 05:00:00", tz="UTC"),]

T5_DO_summmary <- T5DO %>% group_by(Location) %>% summarize(time="T5", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T5_DO_summmary 

#T6
T6DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-08-02 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-08-09 05:00:00", tz="UTC"),]

T6_DO_summmary <- T6DO %>% group_by(Location) %>% summarize(time="T6", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T6_DO_summmary 



stic_decomptime_summaries<- rbind(T1_DO_summmary, T2_DO_summmary, T3_DO_summmary, T4_DO_summmary, T5_DO_summmary, T6_DO_summmary)
write.csv(stic_decomptime_summaries, "expcore_1wkDO_summaries.csv")

```

1-week average DO for all 6 time points
```{r}
#T1 NOTE, Control is missing data extending out to a week, but we assume DO was stable during this period due to flowing conditions
T1DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-06-14 18:00:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-06-16 17:45:00", tz="UTC"),]

T1_DO_summmary <- T1DO %>% group_by(Location) %>% summarize(time="T1", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T1_DO_summmary 

#T2
T2DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-05 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-12 05:00:00", tz="UTC"),]

T2_DO_summmary <- T2DO %>% group_by(Location) %>% summarize(time="T2", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T2_DO_summmary 

#T3
T3DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-18 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-25 05:00:00", tz="UTC"),]

T3_DO_summmary <- T3DO %>% group_by(Location) %>% summarize(time="T3", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T3_DO_summmary 

#T4
T4DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-19 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-26 05:00:00", tz="UTC"),]

T4_DO_summmary <- T4DO %>% group_by(Location) %>% summarize(time="T4", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T4_DO_summmary 

#T5
T5DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-07-23 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-07-30 05:00:00", tz="UTC"),]

T5_DO_summmary <- T5DO %>% group_by(Location) %>% summarize(time="T5", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T5_DO_summmary 

#T6
T6DO <- dd_allDO[dd_allDO$datetime> as.POSIXct("2022-08-02 04:45:00", tz="UTC") & dd_allDO$datetime< as.POSIXct("2022-08-09 05:00:00", tz="UTC"),]

T6_DO_summmary <- T6DO %>% group_by(Location) %>% summarize(time="T6", mean_temp=mean(Temp_C), sd_temp=sd(Temp_C), mean_DO=mean(DO_mgL), sd_DO=sd(DO_mgL))
T6_DO_summmary 



stic_decomptime_summaries<- rbind(T1_DO_summmary, T2_DO_summmary, T3_DO_summmary, T4_DO_summmary, T5_DO_summmary, T6_DO_summmary)
write.csv(stic_decomptime_summaries, "expcore_24hrDO_summaries.csv")

```

```{r}
### calculating daily values for each STIC
####### t1
t1DO_balanced <- t1DO %>%
  ### Shifting timestamps by 6 hours to make "days" start at midnight, for complete 24-hour groupings. Note t1 wass missing the first ~week of data so different than the other periods. 
  mutate(adjusted_date = as.Date(datetime + hours(6))) %>%
  group_by(Location, adjusted_date) %>%
  summarise(#Site=mode(Site),
            #Treatment=Treatment,
            #Habitat=Habitat,
    Daily_avg_DO_mgL = mean(DO_mgL, na.rm = TRUE),
    Diel_DO_change = max(DO_mgL, na.rm = TRUE) - min(DO_mgL, na.rm = TRUE)
  )
t1DO_balanced

t1DO_summary<- t1DO_balanced %>%
    group_by(Location) %>%
              summarise(timeperiod="t1",
                Mean_daily_avg_DO_mgL=mean(Daily_avg_DO_mgL),
                        SD_daily_avg_DO_mgL=sd(Daily_avg_DO_mgL),
                        Mean_instream_diel_DO_change=mean(Diel_DO_change),
                        SD_instream_diel_DO_change=sd(Diel_DO_change)
                        )
t1DO_summary

####### t2a
t2aDO_balanced <- t2aDO %>%
  ### Shifting timestamps by 5 hours to make "days" start at midnight, for complete 24-hour groupings.
  mutate(adjusted_date = as.Date(datetime - hours(5))) %>%
  group_by(Location, adjusted_date) %>%
  summarise(#Site=mode(Site),
            #Treatment=Treatment,
            #Habitat=Habitat,
    Daily_avg_DO_mgL = mean(DO_mgL, na.rm = TRUE),
    Diel_DO_change = max(DO_mgL, na.rm = TRUE) - min(DO_mgL, na.rm = TRUE)
  )
t2aDO_balanced

t2aDO_summary<- t2aDO_balanced %>%
    group_by(Location) %>%
              summarise(timeperiod="t2a",
                Mean_daily_avg_DO_mgL=mean(Daily_avg_DO_mgL),
                        SD_daily_avg_DO_mgL=sd(Daily_avg_DO_mgL),
                        Mean_instream_diel_DO_change=mean(Diel_DO_change),
                        SD_instream_diel_DO_change=sd(Diel_DO_change)
                        )
t2aDO_summary

####### t2b
t2bDO_balanced <- t2bDO %>%
  ### Shifting timestamps by 5 hours to make "days" start at midnight, for complete 24-hour groupings.
  mutate(adjusted_date = as.Date(datetime - hours(5))) %>%
  group_by(Location, adjusted_date) %>%
  summarise(#Site=mode(Site),
            #Treatment=Treatment,
            #Habitat=Habitat,
    Daily_avg_DO_mgL = mean(DO_mgL, na.rm = TRUE),
    Diel_DO_change = max(DO_mgL, na.rm = TRUE) - min(DO_mgL, na.rm = TRUE)
  )
t2bDO_balanced

t2bDO_summary<- t2bDO_balanced %>%
    group_by(Location) %>%
              summarise(timeperiod="t2b",
                Mean_daily_avg_DO_mgL=mean(Daily_avg_DO_mgL),
                        SD_daily_avg_DO_mgL=sd(Daily_avg_DO_mgL),
                        Mean_instream_diel_DO_change=mean(Diel_DO_change),
                        SD_instream_diel_DO_change=sd(Diel_DO_change)
                        )
t2bDO_summary

####### t3
t3DO_balanced <- t3DO %>%
  ### Shifting timestamps by 5 hours to make "days" start at midnight, for complete 24-hour groupings.
  mutate(adjusted_date = as.Date(datetime - hours(5))) %>%
  group_by(Location, adjusted_date) %>%
  summarise(#Site=mode(Site),
            #Treatment=Treatment,
            #Habitat=Habitat,
    Daily_avg_DO_mgL = mean(DO_mgL, na.rm = TRUE),
    Diel_DO_change = max(DO_mgL, na.rm = TRUE) - min(DO_mgL, na.rm = TRUE)
  )
t3DO_balanced

t3DO_summary<- t3DO_balanced %>%
    group_by(Location) %>%
              summarise(timeperiod="t3",
                Mean_daily_avg_DO_mgL=mean(Daily_avg_DO_mgL),
                        SD_daily_avg_DO_mgL=sd(Daily_avg_DO_mgL),
                        Mean_instream_diel_DO_change=mean(Diel_DO_change),
                        SD_instream_diel_DO_change=sd(Diel_DO_change)
                        )
t3DO_summary

TAL_DD_DO_all<- rbind(t1DO_summary,t2aDO_summary,t2bDO_summary,t3DO_summary)
TAL_DD_DO_all
write.csv(TAL_DD_DO_all, "TAL_DD_instream_TAL_DD_DO_all_summaries_06.25.2025.csv")
```

Above we have values calculated for each STIC X period. Below we combine all in-stream STICs for combine averages by treatment (i.e., two riffles and two pools per reach)
```{r}
TAL_DD_DO_all$Treatment<-ifelse(TAL_DD_DO_all$Location=="IU"|TAL_DD_DO_all$Location=="ID","Impact","Control")


instream_summary<- TAL_DD_DO_all %>%
    group_by(Treatment, timeperiod) %>%
              summarise(
                Mean_DO=mean(Mean_daily_avg_DO_mgL),
                        SD_DO=mean(SD_daily_avg_DO_mgL),
                        Mean_diel_DO_change=mean(Mean_instream_diel_DO_change),
                        SD_diel_DO_change=mean(SD_instream_diel_DO_change)
                        )
instream_summary

write.csv(instream_summary, "TAL_DD_instream_DO_summarytab_06.24.2025.csv")

```

## Check
Does DO in the Control reach predict DO in the Impact reach before treatment?
```{r}
Ctabt1 <- t1DO_balanced[t1DO_balanced$Location=="CU"|t1DO_balanced$Location=="CD",] %>%
  group_by(adjusted_date) %>%
  summarise(
    C_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    C_Diel_DO_change = mean(Diel_DO_change),
  )
Ctabt1

Itabt1<- t1DO_balanced[t1DO_balanced$Location=="IU"|t1DO_balanced$Location=="ID",] %>%
  group_by(adjusted_date) %>%
  summarise(
    I_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    I_Diel_DO_change = mean(Diel_DO_change),
  )
Itabt1

CI_tabt1<- merge(Ctabt1, Itabt1, by="adjusted_date")

lmtest<- summary(lm(I_Daily_avg_DO_mgL~C_Daily_avg_DO_mgL, data=CI_tabt1))
lmtest
CI_Daily_avg_DO_mgL <- ggplot(CI_tabt1, aes(x=C_Daily_avg_DO_mgL, y=I_Daily_avg_DO_mgL))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 4))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_Daily_avg_DO_mgL
#########
Ctabt2a <- t2aDO_balanced[t2aDO_balanced$Location=="CU"|t2aDO_balanced$Location=="CD",] %>%
  group_by(adjusted_date) %>%
  summarise(
    C_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    C_Diel_DO_change = mean(Diel_DO_change),
  )
Ctabt2a

Itabt2a<- t2aDO_balanced[t2aDO_balanced$Location=="IU"|t2aDO_balanced$Location=="ID",] %>%
  group_by(adjusted_date) %>%
  summarise(
    I_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    I_Diel_DO_change = mean(Diel_DO_change),
  )
Itabt2a

CI_tabt2a<- merge(Ctabt2a, Itabt2a, by="adjusted_date")

lmtest<- summary(lm(I_Daily_avg_DO_mgL~C_Daily_avg_DO_mgL, data=CI_tabt2a))
lmtest
CI_Daily_avg_DO_mgL <- ggplot(CI_tabt2a, aes(x=C_Daily_avg_DO_mgL, y=I_Daily_avg_DO_mgL))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 4))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_Daily_avg_DO_mgL


########
Ctabt2b <- t2bDO_balanced[t2bDO_balanced$Location=="CU"|t2bDO_balanced$Location=="CD",] %>%
  group_by(adjusted_date) %>%
  summarise(
    C_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    C_Diel_DO_change = mean(Diel_DO_change),
  )
Ctabt2b

Itabt2b<- t2bDO_balanced[t2bDO_balanced$Location=="IU"|t2bDO_balanced$Location=="ID",] %>%
  group_by(adjusted_date) %>%
  summarise(
    I_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    I_Diel_DO_change = mean(Diel_DO_change),
  )
Itabt2b

CI_tabt2b<- merge(Ctabt2b, Itabt2b, by="adjusted_date")

lmtest<- summary(lm(I_Daily_avg_DO_mgL~C_Daily_avg_DO_mgL, data=CI_tabt2b))
lmtest
CI_Daily_avg_DO_mgL <- ggplot(CI_tabt2b, aes(x=C_Daily_avg_DO_mgL, y=I_Daily_avg_DO_mgL))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 4))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_Daily_avg_DO_mgL


#####

Ctabt3 <- t3DO_balanced[t3DO_balanced$Location=="CU"|t3DO_balanced$Location=="CD",] %>%
  group_by(adjusted_date) %>%
  summarise(
    C_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    C_Diel_DO_change = mean(Diel_DO_change),
  )
Ctabt3

Itabt3<- t3DO_balanced[t3DO_balanced$Location=="IU"|t3DO_balanced$Location=="ID",] %>%
  group_by(adjusted_date) %>%
  summarise(
    I_Daily_avg_DO_mgL = mean(Daily_avg_DO_mgL),
    I_Diel_DO_change = mean(Diel_DO_change),
  )
Itabt3

CI_tabt3<- merge(Ctabt3, Itabt3, by="adjusted_date")

lmtest<- summary(lm(I_Daily_avg_DO_mgL~C_Daily_avg_DO_mgL, data=CI_tabt3))
lmtest
CI_Daily_avg_DO_mgL <- ggplot(CI_tabt3, aes(x=C_Daily_avg_DO_mgL, y=I_Daily_avg_DO_mgL))+
    geom_point()+
  geom_smooth(method='lm',color = "black")+
    geom_text(
            aes(x = -Inf, y = Inf, 
                label = paste("R^2=", round(lmtest$r.squared, 3), "   p=", round(lmtest$coefficients[2,4], 4))),
            vjust = 2, 
            hjust = -1,
            size = 4, color = "black")
CI_Daily_avg_DO_mgL
```






### Testing for effects on DO
Now, to return to the daily average DOs from phase t2b, which captures the complete flow reduction phase, we want to test that the drop in dissolved oxygen was significant.

```{}
### Check that impact and contrrol reaches did not differ in dissolved oxygen during 'before' (t1) timeframe:
t1DO_balanced
t1DO_balanced$Treatment<-ifelse(t1DO_balanced$Location=="IU"|t1DO_balanced$Location=="ID","Impact","Control")

### Mixed effects model testing for flow diversion effects on dissolved oxygen
library(lme4)
### Different sensors and dates accounted for as random effects
model <- lmer(Daily_avg_DO_mgL ~ Treatment + (1 | Location) + (1 | adjusted_date), data = t1DO_balanced)
summary(model)
#plot(model)
anova(model)
### Compares model without treatment against model with treatment
anova(model, update(model, ~ . - Treatment))
### Good! p = 0.2412, no ifference between impact and control reach before manipulation.


t2bDO_balanced
t2bDO_balanced$Treatment<-ifelse(t2bDO_balanced$Location=="IU"|t2bDO_balanced$Location=="ID","Impact","Control")

### Mixed effects model testing for flow diversion effects on dissolved oxygen
library(lme4)
### Different sensors and dates accounted for as random effects
model <- lmer(Daily_avg_DO_mgL ~ Treatment + (1 | Location) + (1 | adjusted_date), data = t2bDO_balanced)
summary(model)
plot(model)
anova(model)
### Compares model without treatment against model with treatment
anova(model, update(model, ~ . - Treatment))
### Treatment was ssignificant after accounting for random effects!


t3DO_balanced
t3DO_balanced$Treatment<-ifelse(t3DO_balanced$Location=="IU"|t3DO_balanced$Location=="ID","Impact","Control")

### Mixed effects model testing for flow diversion effects on dissolved oxygen
library(lme4)
### Different sensors and dates accounted for as random effects
model <- lmer(Daily_avg_DO_mgL ~ Treatment + (1 | Location) + (1 | adjusted_date), data = t3DO_balanced)
summary(model)
plot(model)
anova(model)
### Compares model without treatment against model with treatment
anova(model, update(model, ~ . - Treatment))
### Treatment was ssignificant after accounting for random effects!

```

```{r}
t1DO_balanced
t1DO_balanced$Treatment<-ifelse(t1DO_balanced$Location=="IU"|t1DO_balanced$Location=="ID","Impact","Control")
t1DO_balanced$period<-"t1"

t2aDO_balanced
t2aDO_balanced$Treatment<-ifelse(t2aDO_balanced$Location=="IU"|t2aDO_balanced$Location=="ID","Impact","Control")
t2aDO_balanced$period<-"t2a"

t2bDO_balanced
t2bDO_balanced$Treatment<-ifelse(t2bDO_balanced$Location=="IU"|t2bDO_balanced$Location=="ID","Impact","Control")
t2bDO_balanced$period<-"t2b"

t3DO_balanced
t3DO_balanced$Treatment<-ifelse(t3DO_balanced$Location=="IU"|t3DO_balanced$Location=="ID","Impact","Control")
t3DO_balanced$period<-"t3"

tperiod_bound<- rbind(t1DO_balanced,t2aDO_balanced,t2bDO_balanced,t3DO_balanced)

tperiod_bound$Treatment<- as.factor(tperiod_bound$Treatment)
tperiod_bound$period<- as.factor(tperiod_bound$period)

library(multcompView)
#BACI_DO_aov<- aov(Daily_avg_DO_mgL~Treatment*period,data=tperiod_bound)
#summary(BACI_DO_aov)
#tukey<- TukeyHSD(BACI_DO_aov)
#tukey
# compact letter display
#cld <- multcompLetters4(BACI_DO_aov, tukey)
#cld$`Treatment:period`

##### Trying with nonparametric Kruskal Wallis test
tperiod_bound<- tperiod_bound %>% mutate(Treatment_time = paste(Treatment, period, sep = '_'))
kruskal.test(Daily_avg_DO_mgL~Treatment_time,data=tperiod_bound)

library(FSA)
#perform Dunn's Test with Holm correction for p-values
dt<- dunnTest(Daily_avg_DO_mgL~Treatment_time,data=tperiod_bound, method="holm")
library(rcompanion)
dtr<- dt$res
cld <- cldList(comparison = dtr$Comparison,
        p.value    = dtr$P.adj,
        threshold  = 0.05)
cld
```

Diel
```{r}
##### Trying with nonparametric Kruskal Wallis test
#tperiod_bound<- tperiod_bound %>% mutate(Treatment_time = paste(Treatment, period, sep = '_'))
kruskal.test(Diel_DO_change~Treatment_time,data=tperiod_bound)

library(FSA)
#perform Dunn's Test with Holm correction for p-values
dt<- dunnTest(Diel_DO_change~Treatment_time,data=tperiod_bound, method="holm")
library(rcompanion)
dtr<- dt$res
cld <- cldList(comparison = dtr$Comparison,
        p.value    = dtr$P.adj,
        threshold  = 0.05)
cld


```


