---
title: "Talladega weather station"
author: "Charles T. Bond"
date: "11/11/2024"
output: html_document
---

##  Summary
This pipeline is for calculation rainfall for different sampling events in the Talladega watershed from the AIMS project. 

First, I calculate average rainfall in the months, weeks, or days leading up to or during the Talladega synoptic sampling event. 

Second, I calculate average rainfall during the different phases of the Talladega stream flow manipulation experiment. I will also extract the timeseries for each period so that it can be ploted along with other time series data (STICs and DO sensors) from the experiment. 

#####  Note
Timezones for the sensor are in UTC/GMT, so in June of 2022, noon local time (12:00 CST) is recorded as 5 PM (17:00) UTC. 


### Setup
```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/chunk/Chapter_III_Decomp_assays/data_processing/weather")
```

It loads the package before it begins or else it gets the error again
```{r, library}
#library(vegan)
library(tidyverse)
```

## Load the weather station data
```{r}
Tal_weather <- read.csv("/Users/chunk/Chapter_III_Decomp_assays/data_processing/weather/Talladega_TempRain_2022.csv")

head(Tal_weather)

```

```{r}
library(scales)
library(lubridate)
#all_stics$datetime <- as.POSIXlt(all_stics$datetime, tz = "UTC", format = "%Y-%m-%d %H:%M:%OS")
Tal_weather$datetime <- as.POSIXlt(Tal_weather$Timestamp, tz = "UTC", format = "%Y/%m/%d %H:%M")
```


# Talladega synoptic - Rainfall before sampling

Synoptic sampling of the Talladega watershed occured June 9th and 10th of 2022. Heavy storms passed over the watershed in the days before sampling, so we want to quanity rainfall in the days leading up to the storm

```{r}
Tal_syn_rain_days <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-06-07 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-06-09 05:00:00", tz="UTC"),]
sum(Tal_syn_rain_days$Rainfall_mm)
```
### Sum total over the two days before sampling: 11.5 cm rainfall
Over the two-day period before sampling occurred, total rainfall was 11.5 cm. 

That's all I wanted out of those for the synoptic, but for fun, here's a plot of rainfall leading up to the synoptic....
```{r}
Tal_syn_rain_plot <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-02-01 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-06-12 05:00:00", tz="UTC"),]

Tal_syn_rain_plot$datetime<- as.POSIXct(Tal_syn_rain_plot$datetime)

syn_start<- as.POSIXct("2022-06-09 12:00:00", tz="UTC")
syn_end<- as.POSIXct("2022-06-10 23:00:00", tz="UTC")
#tcol<- c("cornflowerblue","brown1")

#library(tidyquant)
TalSpring22_rain_plot <- ggplot(Tal_syn_rain_plot, aes(x=datetime, y=Rainfall_mm))+
    geom_point(size=0.2)+
  scale_shape_manual(values=1)+
  geom_line(aes(linetype='dashed', colour='red'), alpha=0.5, linewidth = 0.3)
TalSpring22_rain_plot

TalSpring22_rain_plot2 <- TalSpring22_rain_plot + 
  geom_vline(xintercept = syn_start, linetype="dotted", linewidth = 0.5, color="blue") +   
  geom_vline(xintercept = syn_end, linetype="dotted", linewidth = 0.5, color="blue")
TalSpring22_rain_plot2
  
lims <- as.POSIXct(strptime(c("2022-04-30 23:30:00", "2022-06-12 04:45:00"), 
                   format = "%Y-%m-%d %H:%M"))

TalSpring22_rain_plot3<- TalSpring22_rain_plot2 +
  scale_x_datetime(labels = date_format("%m-%d"), 
                       # breaks = date_breaks("2 hours"), 
                        limits = lims) #,expand = c(0, 0))
TalSpring22_rain_plot3
```

There we go. The dashed blue lines represents the beginning and end of microbial sampling, showing how sampling occurred immediately after the heavy rain event. Nothing fancy, just nice to have our observations in the field backed up by this weather data, as it will hhelp explain the presence of terrestrial microbes in thhe stream which may have been washed in by the flooding (11.5 cm of rainfall in 2 days is quite a lot of water).


# Talladega experiment - Rainfall during each sampling phase
Now, I will calculate rainfall daily averages and totals for each of four time periods (corresponding with the incubation periods of decomposition assays, i.e., t1, t2a, t2b, t3). 


```{r}
## Note, I set the limits at 
#### midnight of the day decomposition assays were deployed (i.e., just before deployment) to the midnight before retrieval.
t1Tal_weather <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-06-07 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-06-27 05:00:00", tz="UTC"),]

t2aTal_weather <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-06-22 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-07-12 05:00:00", tz="UTC"),]

t2bTal_weather <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-06-27 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-07-22 05:00:00", tz="UTC"),]

t3Tal_weather <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-07-22 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-08-12 05:00:00", tz="UTC"),]
```

```{r}
library(dplyr)
t1_rainsum <- t1Tal_weather %>% summarize(time="t1", Mean_air_temp_C=mean(Temp_C), Total_rainfall_mm=sum(Rainfall_mm), Daily_avg_rainfall_mm=sum(Rainfall_mm)/20)
t1_rainsum

t2a_rainsum <- t2aTal_weather %>% summarize(time="t2a", Mean_air_temp_C=mean(Temp_C), Total_rainfall_mm=sum(Rainfall_mm), Daily_avg_rainfall_mm=sum(Rainfall_mm)/20)
t2a_rainsum

t2b_rainsum <- t2bTal_weather %>% summarize(time="t2b", Mean_air_temp_C=mean(Temp_C), Total_rainfall_mm=sum(Rainfall_mm), Daily_avg_rainfall_mm=sum(Rainfall_mm)/20)
t2b_rainsum

t3_rainsum <- t3Tal_weather %>% summarize(time="t3", Mean_air_temp_C=mean(Temp_C), Total_rainfall_mm=sum(Rainfall_mm), Daily_avg_rainfall_mm=sum(Rainfall_mm)/20)
t3_rainsum

TAL_DD_rainfall_summaries<- rbind(t1_rainsum,t2a_rainsum,t2b_rainsum,t3_rainsum)
write.csv(TAL_DD_rainfall_summaries, "TAL_DD_rainfall_summaries.csv")


```

Now to plot the rainfall over the couse of the experiment...

```{r}
Tal_exp_rain_plot <- Tal_weather[Tal_weather$datetime> as.POSIXct("2022-06-01 04:45:00", tz="UTC") & Tal_weather$datetime< as.POSIXct("2022-08-15 05:00:00", tz="UTC"),]

Tal_exp_rain_plot$datetime<- as.POSIXct(Tal_exp_rain_plot$datetime)
dam_day<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")
undam_day<- as.POSIXct("2022-07-25 19:00:00", tz="UTC")
t1min<- as.POSIXct("2022-06-07 18:00:00", tz="UTC")
t1mid<- as.POSIXct("2022-06-27 18:00:00", tz="UTC") - days(10) 
t1max<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")

t2amin<- as.POSIXct("2022-06-22 18:00:00", tz="UTC")
t2amid<- as.POSIXct("2022-07-12 18:00:00", tz="UTC") - days(10) 
t2amax<- as.POSIXct("2022-07-12 18:00:00", tz="UTC")

t2bmin<- as.POSIXct("2022-06-27 18:00:00", tz="UTC")
t2bmid<- as.POSIXct("2022-07-22 6:00:00", tz="UTC") - days(12) 
t2bmax<- as.POSIXct("2022-07-22 18:00:00", tz="UTC")

t3min<- as.POSIXct("2022-07-22 18:00:00", tz="UTC")
t3mid<- as.POSIXct("2022-08-12 6:00:00", tz="UTC") - days(10)
t3max<- as.POSIXct("2022-08-12 18:00:00", tz="UTC")

#library(tidyquant)
TalExp_rain_plot <- ggplot(Tal_exp_rain_plot, aes(x=datetime, y=Rainfall_mm))+
    geom_point(size=0.2)+
  scale_shape_manual(values=1)+
  geom_line(aes(linetype='dashed', colour='red'), alpha=0.5, linewidth = 0.3)
TalExp_rain_plot

TalExp_rain_plot2 <- TalExp_rain_plot + 
  aes(ymin=-5)+
  geom_vline(xintercept = dam_day, linetype="dotted", linewidth = 0.5, color="blue") +   
  geom_vline(xintercept = undam_day, linetype="dotted", linewidth = 0.5, color="blue") +
    annotate('text', x=dam_day, y=18, label = "\nFlow diversion",  angle=90, size=4, vjust=-0.4)+
  annotate('text', x=undam_day, y=18, label = "\nFlow restoration",  angle=90, size=4, vjust=-0.4)+
  ### rectangles to represent incubation phases
  ## t1
    annotate('rect', xmin = t1min, xmax = t1max, ymin = -1, ymax = -3, alpha = 0.7, fill = 'blue', col = 'black')+
  annotate('text', x=t1mid , y=-2, label = "t1", size=4)+
  ## t2a
    annotate('rect', xmin = t2amin, xmax = t2amax, ymin = -3, ymax = -5, alpha = 0.7, fill = 'yellow', col = 'black')+
  annotate('text', x=t2amid , y=-4, label = "t2a",   size=4)+
  ## t2b
    annotate('rect', xmin = t2bmin, xmax = t2bmax, ymin = -1, ymax = -3, alpha = 0.7, fill = 'red', col = 'black')+
  annotate('text', x=t2bmid , y=-2, label = "t2b",   size=4)+
  ## t3
    annotate('rect', xmin = t3min, xmax = t3max, ymin = -1, ymax = -3, alpha = 0.7, fill = 'green', col = 'black')+
  annotate('text', x=t3mid , y=-2, label = "t3",   size=4)
TalExp_rain_plot2

```

